Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
nudge intro

Linear Time Invariant (LTI) control models represent a broad class of dynamical systems
%modern embedded software, performing highly non-trivial control tasks,
with significant impact in numerous application areas as in 
the life sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}.
Control synthesis for LTI is broadly investigated, 
however the use of digital control architectures adds new challenges due to 
%exacerbated by specific artefacts,  
the effects of finite-precision arithmetic, time discretization, and quantization noise, which are typically introduced 
by Analogue-to-Digital (ADC) and Digital-to-Analogue (DAC) conversion.  
Whilst the research on digital control is well developed~\cite{astrom1997computer}, 
automated and sound control synthesis is a challenging task,  
%Thus, the programming is a key barrier to broad adoption of digital control, 
%and requires considerable expertise.
%Whilst there is a vast literature on validation of control systems,
%the subject of control synthesis has been somewhat restricted in the properties it explores.  
%Traditionally, this focuses mainly on stability %, working typically on continuous domains
particularly when the synthesis objective goes beyond classical stability or tracking requirements. 
%\cite{DBLP:journals/corr/AbateBCCDKK16,sadabadi2016static}, or using switched
%models~\cite{DBLP:conf/emsoft/RavanbakhshS16}. 
Beyond stability, 
recently reachability tools have been developed [cite SPACEx, Phaver, and others], 
however they have not been employed towards control synthesis. 
%\todo{why do we cite this paper \cite{cimatti2013parameter}?what is the relationship with our work? }
% when discretising the state-space for verification and
%parameter synthesis~\cite{cimatti2013parameter}.

>>>>

Linear Time Invariant (LTI) models represent a broad class of dynamical systems
%modern embedded software, performing highly non-trivial control tasks,
with significant impact in numerous application areas as in 
the life sciences, robotics, and engineering~\cite{astrom1997computer,Franklin15}.
Synthesis of controllers for LTI models is broadly investigated, 
however the use of digital control architectures adds new challenges due to 
the effects of finite-precision arithmetic, time discretization, and quantization noise, which are typically introduced 
by Analogue-to-Digital (ADC) and Digital-to-Analogue (DAC) conversion.  
While research on digital control is well developed~\cite{astrom1997computer}, 
automated and sound control synthesis is challenging, 
%Thus, the programming is a key barrier to broad adoption of digital control, 
%and requires considerable expertise.
%Whilst there is a vast literature on validation of control systems,
%the subject of control synthesis has been somewhat restricted in the properties it explores.  
%Traditionally, this focuses mainly on stability %, working typically on continuous domains
particularly when the synthesis objective goes beyond classical stability or tracking requirements. 
%\cite{DBLP:journals/corr/AbateBCCDKK16,sadabadi2016static}, or using switched
%models~\cite{DBLP:conf/emsoft/RavanbakhshS16}. 
Beyond stability, recently reachability tools have been developed [cite
SPACEx, Phaver, and others], however they have not been employed towards
control synthesis.
%\todo{why do we cite this paper \cite{cimatti2013parameter}?what is the relationship with our work? }
% when discretising the state-space for verification and
%parameter synthesis~\cite{cimatti2013parameter}.
